\input{../../header.tex}


\titleandsubtitle{CNC Interface \\ Software Requirements Specification}{Submitted in Partial Fulfillment of the Requirements for the B.Sc. Degree, \\ Computer and Electronics Engineering, College of Engineering, \\ University of Nebraska \\ Peter Kiewit Institute, Omaha, Nebraska, U.S.A}

\begin{document}
\maketitle
\tableofcontents
\tableoffiguresandtables
\begin{acronym}
\newacronym{3d}{3-D}{Three-Dimensional}
\newacronym{ceen}{CEEN}{Computer and Electronics Engineering}
\newacronym{ceenc}{\textsc{CeeNC}}{CEEN Numerical Controller}
\newacronym{cnc}{CNC}{Computer Numerical Control}
\newacronym{i2c}{I$^2$C}{Inter-Integrated Circuit}
\newacronym{os}{OS}{Operating System}
\newacronym{pi}{Pi}{Raspberry Pi}
\newacronym{rom}{ROM}{Read-Only Memory}
\newacronym{spi}{SPI}{Serial Peripheral Interface}
\newacronym{srs}{SRS}{Software Requirements Specification}
\newacronym{tcpip}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
\newacronym{ti}{TI}{Texas Instruments}
\newacronym{uart}{UART}{Universal Asynchronous Receiver/Transmitter}
\end{acronym}


\chapter{Introduction}
This section provides an overview of the purpose and scope of the \gls{srs} and introduces the acronyms used within the report.
\section{Purpose}
The purpose of the \gls{srs} is to define the requirements for the software portion of the \gls{ceenc}.
This \gls{srs} was developed in conjuntion with a prototype as part of IEEE Std. 830-1998 section 4.6 \cite[p.~9]{std830}.
This document is intended for anyone that might work on the software at any point in the future.
\section{Scope}
The \gls{ceenc} is a network enabled, configurable \gls{cnc}interface that is compact and affordable.
The \gls{ceenc} accurately and safely drives a set of motors based on G-code files uploaded over the network.
The file will be interpreted in a single board computer and a microcontroller.
 The microcontroller then correctly controls the motors through a motor driver board.
The system can be used to drive a variety of devices, for example a \gls{cnc} Mill or a \gls{3d} printer, through a web interface.
\newline
\newline
The software requirements for this project include a G-code interpreter, ...
\newline
\newline
This subsection should
\newline
a) Identify the software product(s) to be produced by name (e.g., Host DBMS, Report Generator, etc.);
\newline
b) Explain what the software product(s) will, and, if necessary, will not do;
\newline
c) Describe the application of the software being speciÞed, including relevant beneÞts, objectives, and
goals;
\newline
d) Be consistent with similar statements in higher-level specifications (e.g., the system requirements
specification), if they exist.
\section{Definitions, Acronyms, and Abbreviations}
\hspace{12 pt}
\begin{acronym}
\newacronym{3d}{3-D}{Three-Dimensional}
\newacronym{ceen}{CEEN}{Computer and Electronics Engineering}
\newacronym{ceenc}{\textsc{CeeNC}}{CEEN Numerical Controller}
\newacronym{cnc}{CNC}{Computer Numerical Control}
\newacronym{i2c}{I$^2$C}{Inter-Integrated Circuit}
\newacronym{spi}{SPI}{Serial Peripheral Interface}
\newacronym{srs}{SRS}{Software Requirements Specification}
\newacronym{tcpip}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
\newacronym{uart}{UART}{Universal Asynchronous Receiver/Transmitter}
\end{acronym}

\section{References}
%\input{bibliography.tex}
%http://www.cse.chalmers.se/~feldt/courses/reqeng/examples/srs_example_2010_group2.pdf

\section{Overview}
The rest of the \gls{srs} contains sections for the overall description and specific requirements for the software.
The overall description describes how the system will funtion and interact.
It will also describe who the stakeholders are and their roles as well as system constraints and assumptions.
The specific requirements section will explain the requirements of the software in a more detailed manner. 

\input{overall-description.tex}
\input{specific-requirements.tex}

\end{document}